Global Illumination for Fun and Profit

### 2022-02-22 paper.qmd
use CSL/citeproc instead of natbib

---
# Quarto-specific stuff you probably don't want to change for now
pdf-engine: pdflatex
documentclass: vgtc
cite-method: natbib
natbiboptions: square, numbers
format:
  pdf:
    template: vgtc-quarto-template/tvcg.latex
  # FIXME how does keep_tex work in the yaml?
  latex:
    template: vgtc-quarto-template/tvcg.latex
  #  Uncomment the line below to also generate an HTML version
  html: default

# Stuff you'll want to change
title: Global Illumination for Fun and Profit
shortauthortitle: "Biv et al.: Global Illumination for Fun and Profit"
author:
  - name: Roy G. Biv
    institution: Starbucks Research
    email: "roy.g.biv@aol.com"
  - name: Ed Grimley
    institution: Grimley Widgets, Inc.
    email: "ed.grimley@aol.com"
  - name: Martha Stewart
    institution: Martha Stewart Enterprises at Microsoft Research
    email: "martha.stewart@marthastewart.com"

# If you are submitting a paper to a conference for review with a double
# blind reviewing process, please uncomment the line below and use your
# OnlineID. 
# online-id: 987654321

@@

abstract: |
  Duis autem vel eum iriure dolor in hendrerit in vulputate
  velit esse molestie consequat, vel illum dolore eu feugiat nulla
  facilisis at vero eros et accumsan et iusto odio dignissim qui blandit
  praesent luptatum zzril delenit augue duis dolore te feugait nulla
  facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit,
  sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna
  aliquam erat volutpat. Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper
  suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis autem
  vel eum iriure dolor in hendrerit in vulputate velit esse molestie
  consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et
  accumsan et iusto odio dignissim qui blandit praesent luptatum zzril
  delenit augue duis dolore te feugait nulla facilisi.
bibliography: paper.bib
firstsection: Introduction
keyword:
  - Radiosity
  - global illumination
  - constant time
---

@@

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
dolore magna aliquyam erat, sed diam
voluptua [@Kitware:2003,Max:1995:OMF]. At vero eos et accusam et
justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
invidunt ut labore et dolore magna aliquyam erat, sed diam
voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est.

@@

[^1]: The algorithm behind Marching Cubes by @Lorensen:1987:MCA had
    already been described by @Wyvill:1986:DSS a
    year earlier.

@@

Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper
suscipit lobortis nisl ut aliquip ex ea commodo
consequat, by @Nielson:1991:TAD. Duis autem vel eum iriure dolor in
hendrerit in vulputate velit esse molestie consequat, vel illum dolore
eu feugiat nulla facilisis at vero eros et accumsan et iusto odio
dignissim qui blandit praesent luptatum zzril delenit augue duis
dolore te feugait nulla facilisi.

@@

As @Kindlmann:1999:SAG has shown, it is possible to generate transfer functions semi-automatically.

@@

>>>>

---
# Quarto-specific stuff you probably don't want to change for now
pdf-engine: pdflatex
csl: vgtc-tvcg.csl
link-citations: true

################################################################################

format:
  pdf:
    template: vgtc-quarto-template/tvcg.latex
#  Uncomment the line below to also generate an HTML version
#  html: default

################################################################################
# Paper metadata

title: Global Illumination for Fun and Profit
shortauthortitle: "Biv et al.: Global Illumination for Fun and Profit"
author:
  - name: Roy G. Biv
    institution: Starbucks Research
    email: "roy.g.biv@aol.com"
  - name: Ed Grimley
    institution: Grimley Widgets, Inc.
    email: "ed.grimley@aol.com"
  - name: Martha Stewart
    institution: Martha Stewart Enterprises at Microsoft Research
    email: "martha.stewart@marthastewart.com"

# If you are submitting a paper to a conference for review with a double
# blind reviewing process, please uncomment the line below and use your
# OnlineID. 
#online-id: 1337
# comment this line for final version
review: true

@@

# Uncomment this to add a teaser to your paper

teaser:
  image-options: width=\linewidth
  image: CypressView.jpg
  caption: |
    In the Clouds: Vancouver from Cypress Mountain. Note that the
    teaser may not be wider than the abstract block.
  label: fig-teaser

abstract: |
  Duis autem vel eum iriure dolor in hendrerit in vulputate
  velit esse molestie consequat, vel illum dolore eu feugiat nulla
  facilisis at vero eros et accumsan et iusto odio dignissim qui blandit
  praesent luptatum zzril delenit augue duis dolore te feugait nulla
  facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit,
  sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna
  aliquam erat volutpat. Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper
  suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis autem
  vel eum iriure dolor in hendrerit in vulputate velit esse molestie
  consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et
  accumsan et iusto odio dignissim qui blandit praesent luptatum zzril
  delenit augue duis dolore te feugait nulla facilisi.
keyword:
  - Radiosity
  - global illumination
  - constant time
firstsection: Introduction
bibliography: paper.bib
---

@@

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
dolore magna aliquyam erat, sed diam
voluptua [@Kitware:2003,@Max:1995:OMF]. At vero eos et accusam et
justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
invidunt ut labore et dolore magna aliquyam erat, sed diam
voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est.

@@

[^1]: The algorithm behind Marching Cubes by Lorensen et al. @Lorensen:1987:MCA had
    already been described by Wyvill et al. a
    year earlier [@Wyvill:1986:DSS].

@@

Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper
suscipit lobortis nisl ut aliquip ex ea commodo
consequat [@Nielson:1991:TAD]. Duis autem vel eum iriure dolor in
hendrerit in vulputate velit esse molestie consequat, vel illum dolore
eu feugiat nulla facilisis at vero eros et accumsan et iusto odio
dignissim qui blandit praesent luptatum zzril delenit augue duis
dolore te feugait nulla facilisi.

@@

As Kindlmann has shown, it is possible to generate transfer functions semi-automatically [@Kindlmann:1999:SAG].

@@

# References {.unnumbered}
